|

### 2023-06-27 paper/paper.qmd
Remove TODO
Add abstract and appendix

---
title: |
    | *'Zijt gij dat of bent gij dat?'*
    | Een alternantiestudie van de tweede persoon enkelvoud van *zijn* in Vlaamse tussentaal
author:
  - name: Anthe Sevenants
    email: anthe.sevenants@kuleuven.be
    orcid: 0000-0002-5055-770X
    affiliations:
      - name: KU Leuven
format: 
   html:
      df-print: kable
include-in-header:
  - text: |
      <style>
      h1 {
        text-align: center;
      }
      </style>
editor: visual
title-block-banner: true
bibliography: references.bib
toc: true
toc-depth: 4
toc-location: left
tbl-cap-location: bottom
fig-cap-location: bottom
number-sections: true
reference-location: margin
csl: chicago-author-date.csl
execute:
  echo: false
lang: nl
---

@@

![Een visuele voorstelling van de resultaten van het geografische model TODO vervangen](heatmap.png){#fig-gam-map}

@@

>>>>

---
title: |
        '*Zijt* gij dat of *bent* gij dat?'
subtitle: Een alternantiestudie van de tweede persoon enkelvoud van *zijn* in Vlaamse tussentaal
abstract: |
  In Colloquial Belgium Dutch (QBD) a special form of the second person singular of *zijn* ('to be') has appeared: *gij bent*. This construction blends the historically traditional form *gij zijt* with the more formal Standard Dutch *bent* from *jij bent*. Though the construction now appears in QBD, it is said to originate from northern Antwerp dialects. A logistic regression analysis and general additive model of colloquial Flemish tweets show that *gij bent* is popular only in the Brabant dialect area and that usage is highest in the northern Antwerp area. In addition, it is found that *gij bent* is more likely to appear in tweets with general statements rather than conversations, which hints at a formality difference. Tweets thought to come from women also feature more *gij bent*. It is plausible that *gij bent*, though it does not originate from a leading language area, was able to spread throughout the Brabant dialect area because of a formality reinterpretation. While the form likely originates from the northern Antwerp dialects, it might have been reinterpreted as an innovative, hybrid form in QBD, but only in the Brabant area. There is currently no evidence that *gij bent* has spread to other dialect areas.
abstract-title: Abstract
author:
  - name: Anthe Sevenants
    email: anthe.sevenants@kuleuven.be
    orcid: 0000-0002-5055-770X
    affiliations:
      - name: KU Leuven
format: 
   html:
      df-print: kable
include-in-header:
  - text: |
      <style>
      h1 {
        text-align: center;
      }
      </style>
editor: visual
css: paper.css
title-block-banner: true
bibliography: references.bib
toc: true
toc-depth: 4
toc-location: left
tbl-cap-location: bottom
fig-cap-location: bottom
number-sections: true
reference-location: margin
csl: chicago-author-date.csl
execute:
  echo: false
lang: nl
---

@@

![Een visuele voorstelling van de resultaten van het geografische model](heatmap.png){#fig-gam-map}

@@

## Appendix {#appendix .appendix}

**Jaarbeperking ('YEAR_SNIPPET')**

```{.code-overflow-wrap}
since:{YEAR}-01-01 until:{YEAR}-12-31
```

**Query voor *gij bent***

```{.code-overflow-wrap}
(ge OR gij OR gy bent) OR \"bende gij\" -je -jij {YEAR_SNIPPET} lang:nl
```

**Query voor *gij zijt***

```{.code-overflow-wrap}
(ge OR gij OR gy zijt) OR (ge OR gij OR gy zyt) OR (zijde ge OR zijde gij OR zijde gy) OR (zyde ge OR zyde gij OR zyde gy) OR (zedde ge OR zedde gij OR zedde gy) {YEAR_SNIPPET} -je -jij lang:nl
```
